---
title: "SDS 313 HW"
author: "Samuel Li"
date: "4/14/25"
output: pdf_document

---

[https://github.com/SamuelLi1225/Homework8](https://github.com/SamuelLi1225/Homework8) 

```{r echo=FALSE}
creatinine <- read.csv("creatinine.csv")

model <- lm(creatclear ~ age, data = creatinine)

#1.A
summary(model)
147.81292 - (0.61982 * 55) 


#1.B Slope of the regression line

summary(model)

#1.C
res_40 <- 135 - predict(model, newdata = data.frame(age = 40))
res_60 <- 112 - predict(model, newdata = data.frame(age = 60))

res_40
res_60



```
#1.A

From the model, the y intercept was 147.81292 and the slope was -0.61982, so i subtracted the intercept by 55 times the slope to predict the levels for 55 year olds. My prediction was 113.7228

#1.B

The model states that the slope is -0.61892. Creatinine clearance decreases by about 0.62 ml/min per year.

#1.C

The 40 year old has a residual of 11.97972 and the 60 year old has a residual of 1.376035. This means that the 40 year old is predicted to be healthier as he has a higher residual. 


```{r echo = FALSE}
library(mosaic)
library(ggplot2)

#1,2
covid <- read.csv("covid.csv")
covid <- subset(covid, deaths > 0)
covid$log_deaths <- log(covid$deaths)



italy <- subset(covid, country == "Italy")
spain <- subset(covid, country == "Spain")

model_italy <- lm(log_deaths ~ days_since_first_death, data = italy)
model_spain <- lm(log_deaths ~ days_since_first_death, data = spain)
summary(model_italy)
summary(model_spain)

doubling_italy <- log(2) / 0.18322
doubling_spain <- log(2) / 0.27624



doubling_italy
doubling_spain


#CI 

# ITALY
boot_italy <- do(1000) * 
  coef(lm(log_deaths ~ days_since_first_death, data = resample(italy)))[[2]]

ci_growth_italy <- quantile(boot_italy[[1]], c(0.025, 0.975), na.rm = TRUE)
ci_doubling_italy <- log(2) / ci_growth_italy

# SPAIN
boot_spain <- do(1000) * 
  coef(lm(log_deaths ~ days_since_first_death, data = resample(spain)))[[2]]

ci_growth_spain <- quantile(boot_spain[[1]], c(0.025, 0.975), na.rm = TRUE)
ci_doubling_spain <- log(2) / ci_growth_spain



ci_growth_italy
ci_doubling_italy
ci_growth_spain
ci_doubling_spain



#2.3


library(ggplot2)

# Load and clean the data if not already done
covid <- read.csv("covid.csv")
covid <- subset(covid, deaths > 0)  

ggplot(covid, aes(x = days_since_first_death, y = deaths, color = country)) +
  geom_line(size = 1) +
  labs(
    title = "Reported COVID-19 Deaths Over Time",
    x = "Days Since First Death",
    y = "Daily Deaths"
  ) +
  theme_minimal() +
  theme(legend.title = element_blank())




```

#2.1

Italy Growth Rate: 0.183, deaths increased by 18.3% a day 
Italy Doubling Time: About 3.8 days to double 
95% Bootstrapped CI: 
We are 95% confident that the true growth rate is between [0.160, 0.209]
We are 95% confident that the true doubling time is between [4.4, 3.4]

#2.2
Spain Growth Rate: 0.276, deaths increased by 27.6% a day 
Spain Doubling Time: About 2.5 days to double 
95% Bootstrapped CI: 
We are 95% confident that the true growth rate is between [0.232, 0.317]
We are 95% confident that the true doubling time is between [3.0, 2.2]

```{r echo = FALSE}
library(mosaic)
milk <- read.csv("milk.csv")
milk <- subset(milk, price > 0 & sales > 0)
milk$log_price <- log(milk$price)
milk$log_sales <- log(milk$sales)

model <- lm(log_sales ~ log_price, data = milk)
elasticity <- coef(model)[2]

boot <- do(1000) * {
  data.frame(slope = coef(lm(log_sales ~ log_price, data = resample(milk)))[2])
}

elasticities <- boot$slope
elasticities <- elasticities[!is.na(elasticities)]
ci <- quantile(elasticities, c(0.025, 0.975))

elasticity
ci






```

#3
log(sales) ~ log(price) was my equation.
The estimated price elasticity demand is about -1.62, this means a 1% increase in milk price leads to approximately a 1.62% decrease in sales. This suggests that milk demand is elastic.

95% confidence interval of [-1.77, -1.45] elasticity estimate.
